On X-ray emission from Fast Blue Optical Transients

### 2023-06-25 papers/FBOTcompton/fbotcompton.tex
electrons energy

>>>>

\begin{equation}
R_{ik}-\frac{1}{2} g_{ik}R=\frac{8\pi G}{c^4} T_{ik}
\end{equation}
\begin{equation}
A(\gamma_{\alpha\gamma}\gamma_{\beta\delta} - \gamma_{\alpha\delta}\gamma_{\beta\gamma})
\end{equation}
\begin{equation}
P^\gamma_{\alpha\gamma\beta}=2A\gamma_{\alpha\beta}
\end{equation}
\begin{equation}
dl^2 = dx_1^2+dx_2^2+dx_3^2+\frac{(x_1 dx_1 + x_2 dx_2 +x_3 dx_3)^2}{a^2-x_1^2-x_2^2-x_3^2}
\end{equation}
\begin{equation}
\gamma_{\alpha\beta}=\delta_{\alpha\beta}+x_\alpha x_\beta/a^2
\end{equation}
\begin{equation}
dl^2=dr^2/(1-r^2/a^2)+r^2(sin^2 \theta d\phi^2+d\theta^2)
\end{equation}
\begin{equation}
dl^2=a^2(d\chi^2 + sin^2\chi(sin^2 \theta d\phi^2+d\theta^2))
\end{equation}
\begin{equation}
ds^2 = c^2 dt^2-dl^2 = c^2 dt^2 – a(t)^2(d\chi^2 + sin^2\chi(sin^2 \theta d\phi^2+d\theta^2))
\end{equation}
\begin{equation}
ds^2 = c^2 dt^2-dl^2 = a(\eta)^2( d\eta^2 - d\chi^2 - sin^2\chi(sin^2 \theta d\phi^2+d\theta^2))
\end{equation}
\begin{equation}
R^\chi_\chi = R^\theta_\theta = R^\phi_\phi= -(2 a^2 + (da/d\eta)^2 + a d^2a/d\eta^2)/a^4
\end{equation}
\begin{equation}
R^\eta_\eta=3*((da/d\eta)^2-a da/d\eta)/a^4
\end{equation}
\begin{equation}
R=-6(a+d^2a/d\eta^2)/a^3
\end{equation}
\begin{equation}
3(a^2+d^2a/d\eta^2)/a^4 = 8 \pi G \epsilon/c^4
\end{equation}
\begin{equation}
d\epsilon=-(\epsilon + p)dV/V
\end{equation}
\begin{equation}
3 ln~a = -\int d\epsilon/(\epsilon + p)
\end{equation}
\begin{equation}
a=a_0(1 – cos \eta)
\end{equation}
\begin{equation}
t=\frac{a_0}{c} (\eta – sin \eta)
\end{equation}
\begin{equation}
a_0 = 2GM/3\pi^2
\end{equation}
\begin{equation}
R_{ik}-1/2 g_{ik}R=8\pi G/c^4 T_{ik}-\Lambda g_{ik}
\end{equation}
